%-------------------------
% Resume
% Author : Sangshik Park
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/sangshik-park-b14774a9/}{\Large Sangshik Park}} & Visa Status: US Permanent Resident\\
  \href{https://www.linkedin.com/in/sangshik-park-b14774a9/}{https://www.linkedin.com/in/sangshik-park-b14774a9/} & Email: \href{mailto:ss127.park@gmail.com}{ss127.parkk@gmail.com} \\ 
  & Mobile: +1-617-515-9675
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Rockley Photonics}{Irvine, CA}
    {Senior Staff Algorithm Engineer}{February 2022 - }
    \resumeItemListStart
        \resumeItem{Blood Pressure}
          {Developed a blood pressure estimation algorithm using speckleplethysmography (SPG) signal.}
      \resumeItemListEnd
    \resumeSubheading
    {Imperative Care}{Campbell, CA}
    {Principal Data Scientist}{March 2020 - February 2022}
    \resumeItemListStart
        \resumeItem{Anomaly Detection for Stroke Onset}
          {Developed a autoencoder-based anomaly detection algorithm using heart rate variability features to visualize stroke onset.}
        \resumeItem{Peripheral Vasomotor Activity Assessment}
          {Developed a PPG-based vasodilation detection algorithm using pulse wave analysis to improve stroke detection accuracy.}
        \resumeItem{Respiratory Rate}
          {Developed a PPG-based respiratory rate algorithm using particle filter and autoregressive method that ourperforms traditional respiratory rate estimation methods.}
      \resumeItemListEnd

    \resumeSubheading{Beddr}{Mountain View, CA}{Data Scientist}{May 2019 - February 2020}
      \resumeItemListStart
      \resumeItem{Wear-time Detection}
      {Designed a neural network model to accurately detect whether the device is in contact with the skin or not.}
      \resumeItem{SpO2}
      {Improved SpO2 accuracy using a weighted average algorithm and signal quality index.}
      \resumeItem{Heart Rate}
      {Improved heart rate accuracy by removing motion artifacts from the signal using adaptive filters.}
    \resumeItemListEnd

    \resumeSubheading
      {Nulogix Health}{Boston, MA}
      {Machine Learning Engineer}{August 2018 - May 2019}
      \resumeItemListStart
        \resumeItem{Medical Billing Prediction}
        {Developed an AI-based medical billing model that predicts the amount of deductible, copay, and coinsurance.}
        \resumeItem{Anomaly Detection for Chest X-ray}
        {Developed a convolutional autoencoder-based model to extract features from chest X-ray images and used t-SNE to differentiate between normal and abnormal images.}
      \resumeItemListEnd

    \resumeSubheading
      {Samsung Electronics}{Gyeonggi, Korea}
      {Senior Algorithm Engineer}{November 2014 - December 2017}
      \resumeItemListStart
      \resumeItem{Body Composition Analysis}
      {Designed a regression model using bioelectrical impedance to estimate body fat and skeletal muscle mass. Integrated this model into TomTom Touch.}
      \resumeItem{Sleep Stage Classification}
      {Developed a neural network model that utilizes ECG RR interval and peak amplitude to classify sleep stages.}
      \resumeItem{Motion Artifact Removal for Photoplethysmography}
      {Developed a PPG motion artifact removal algorithm using singular spectrum analysis.}
      \resumeItem{Heart Rate and Heart Rate Variability}
      {Developed an ECG peak detection algorithm to estimate heart rate and heart rate variability. Integrated this algorithm into Samsung's ECG S-Patch.}
      \resumeItemListEnd
    
      \resumeSubheading
      {LG Electronics}{Seoul, Korea}
      {Research Engineer}{July 2012 - July 2014}
      \resumeItemListStart
      \resumeItem{Ultrasound Software Beamforming}{Developed a software-based plane wave beamforming algorithm for an ultrasound device.}
      \resumeItem{Optical Coherence Tomography for Dermatology}{Developed an algorithm for detecting structural changes related to skin aging, including collagen, dermal density, and wrinkles using optical coherence tomography.}
      \resumeItemListEnd

      \resumeSubheading
      {Samsung Medison}{Seoul, Korea}
      {Associate Research Engineer}{June 2007 - December 2010}
      \resumeItemListStart
      \resumeItem{ElastoScan - Freehand Elastography}
      {Developed a real-time algorithm for estimating displacement and strain in freehand ultrasound elastography. Implemented noise removal algorithms including adaptive persistence and axial dropout correction.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science (Specialization: Machine Learning)}{2020 -- }
    \resumeSubheading
      {Seoul National University}{Korea}
      {Master of Science in Electrical Engineering and Computer Science}{2005 -- 2007}
    \resumeSubheading
      {Kyunghee University}{Korea}
      {Bachelor of Engineering in Electronics;  GPA: 4.021/4.3}{2001 -- 2005}
  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Science}{}
      {Python, Pandas, Numpy, Scikit-learn, SciPy, Tensorflow, Pytorch, TensorRT}{}
    \resumeSubheading
      {Others}{}
      {MATLAB, C, R, Git, SQL, AWS}{}
  \resumeSubHeadingListEnd

%--------HONORS AND AWARDS------------
\section{Honors and Awards}
  \resumeSubHeadingListStart
    \item{
      \textbf{2002}{ Korea Research Foundation Scholarship - Full Scholarship}
    }
    \item{
      \textbf{2003}{ Korea Research Foundation Scholarship - Full Scholarship}
    }
    \item{
      \textbf{2004}{ Korea Research Foundation Scholarship - Full Scholarship}
    }
    \item{
      \textbf{2005}{ Award for Excellent Records (GPA: 4.021/4.3)}
    }
    \item{
      \textbf{2005}{ Seoul National University Scholarship}
    }
    \item{
      \textbf{2006}{ Samsung Medison Scholarship}
    }

  \resumeSubHeadingListEnd

  %--------PATENTS------------
\section{Patents}
\resumeSubHeadingListStart
\item{
    \textbf{US 20210106238}{ Systems and methods for multivariate stroke detection}
  }
  \item{
    \textbf{US 20180333075}{ Respiratory Rate Measuring Method and Apparatus, and Wearable Device}
  }
  \item{
    \textbf{US 20180359112}{ Home Device Control Device and Operation Method Thereof}
  }
  \item{
    \textbf{US 20180228432}{ Method of Providing Service based on Biometric Information and Wearable Electronic Device}
  }
  \item{
    \textbf{US 8337406 / EP 2189116}{ Adaptive Persistence Processing of Elastic Images}
  }
  \item{
    \textbf{US 8503714}{ Dropout Correction in Ultrasound Strain Imaging}
  }
  \item{
    \textbf{US 9125618}{ Providing an Elastic Image in an Ultrasound System}
  }
  \item{
    \textbf{US 8834374 / EP 2289420}{ Setting an Optimal Image Parameter in an Ultrasound System}
  }
  \item{
    \textbf{US 9289190}{ Ultrasound Strain Imaging via Pixel Frame and Window Correlation}
  }

\resumeSubHeadingListEnd

  %--------PUBLICATIONS------------
  \section{Publications}
  \resumeSubHeadingListStart
    \item{
      \textbf{}{Speckle Reduction in Optical Coherence Tomography Images via Dynamic Infinite-Impulse-Response Filtering, J Lee, SS Park, JH Chung, SPIE, 2014}
    }
    
  
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
